% Build: cd docs/reports/reconstruction/methods && latexmk -xelatex pdc_reco_literature_and_air_ms_gap_20260426.tex
\documentclass[a4paper, 11pt]{article}

\usepackage[margin=2.4cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,calc}
\usepackage{longtable}
\usepackage{tabularx}

\definecolor{goodgreen}{RGB}{34,139,34}
\definecolor{warnred}{RGB}{200,50,50}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black,
}

\title{\textbf{PDC Reconstruction Literature Survey \\ and SAMURAI Terminal Air-MS Gap Analysis}}
\author{Baiting Tian \\ RIKEN Nishina Center / DPOL Experiment}
\date{2026-04-26}

\begin{document}
\maketitle
\tableofcontents
\clearpage

\section{TL;DR}
This document surveys the published reference frame for the SAMURAI PDC1/PDC2 drift-chamber chain and contrasts it with our current Geant4 reconstruction performance, in order to localise the air multiple-scattering gap that drives our PDC2 spatial resolution one order of magnitude above design.

\begin{itemize}
  \item \textbf{Reference frame.} The PDC1/PDC2 chain has no dedicated peer-reviewed publication, and an April 2026 audit (see §3.2 and §7.3) found no PhD thesis that contains a PDC reconstruction chapter either. The canonical references that do exist are the SAMURAI overview paper by Kobayashi et al., Nucl. Instr. Meth. B \textbf{317}, 294--304 (2013) §3.4\footnote{\label{fn:kobayashi2013}T.~Kobayashi et al., Nucl. Instr. Meth. B \textbf{317}, 294--304 (2013), DOI: \href{https://doi.org/10.1016/j.nimb.2013.05.089}{10.1016/j.nimb.2013.05.089}.} and the RIKEN internal technical note \texttt{Detector-PDC.pdf}\footnote{\label{fn:detectorpdc}RIKEN Nishina Center, \emph{Detector-PDC} technical note, \url{https://www.nishina.riken.jp/ribf/SAMURAI/image/Detector-PDC.pdf}.}; both cover hardware specification rather than reconstruction performance.
  \item \textbf{Design specifications.} Combining Kobayashi 2013 §3.4\footref{fn:kobayashi2013} with the SAMURAI 2012 construction proposal\footnote{\label{fn:samurai2012}SAMURAI Collaboration, \emph{SAMURAI Construction Proposal} (2012), \url{https://ribf.riken.jp/SAMURAI/120425_SAMURAIConstProp.pdf}.}, the PDC1/PDC2 chain targets 1~mm position resolution, 2~mrad angular resolution, and 0.8\% relative momentum resolution ($\Delta p/p$). Commissioning RI-beam runs reached $\Delta p/p \approx 1/1500$\footref{fn:kobayashi2013}; the original proton-mode design value is $\Delta p/p \approx 1/700$ as quoted in the RIBF-TAC05 (2005) construction proposal\footnote{\label{fn:ribftac05}SAMURAI Collaboration, \emph{RIBF-TAC05 SAMURAI construction proposal} (2005), \url{https://ribf.riken.jp/RIBF-TAC05/10_SAMURAI.pdf}.}.
  \item \textbf{Our measured $\sigma_y$(PDC2).} In our Geant4 + reconstruction chain we observe $\sigma_y(\text{PDC2}) = 12.83$--$14.93$~mm in the all-air configuration, $6.80$--$8.21$~mm when Region~A (dipole cavity + beam pipe) is set to vacuum (\texttt{beamline\_vacuum}), and approximately $1.0$~mm in the all-vacuum configuration\footnote{\label{fn:msablation}See \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_mixed\_20260422\_zh.md} §4.}. The realistic-air values sit roughly an order of magnitude away from the 1~mm hardware design specification\footref{fn:kobayashi2013}.
  \item \textbf{Air MS dominates and the configuration choice matters.} A quadrature decomposition\footref{fn:msablation} attributes the all-air budget to $\sigma_A \approx 11.19$~mm from Region~A (cavity + beam pipe, $\sim$4.3~m) and $\sigma_B \approx 7.43$~mm from Region~B (Exit Window $\to$ PDCs, $\sim$2~m). The stage~D inputs from the same memo\footnote{See \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_mixed\_20260422\_zh.md} §6.} give $\sigma_y(\text{PDC2}) = 7.49$~mm if Region~A is vacuum and $\sigma_y(\text{PDC2}) = 13.50$~mm if both Region~A and Region~B are air. Whether Region~A is air or vacuum during the experiment is therefore a configuration question that selects between these two values; this document does not assert which one corresponds to the actual run.
\end{itemize}

See §6 for proposed action items.

\section{The problem: air multiple scattering at the SAMURAI terminal}
% [content from Task 3]
% NOTE: skipped TikZ flight-path sketch in favour of explicit prose; the geometry
%       is captured numerically by the world/local coordinates and the Region A/B
%       definitions below, and a hand-drawn diagram risks introducing inaccuracies.

\subsection{Geometry of the proton flight path}
The deuteron target sits at world coordinates $(-12.488, 0.0009, -1069.458)$~mm, which corresponds to yoke-local coordinates $(-545.5, 0, -919.9)$~mm under the $-30^\circ$ yoke rotation about $Y$\footnote{\label{fn:msablation_geom}See \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_mixed\_20260422\_zh.md} §1.1--§1.3 for coordinates, yoke rotation, and Region A/B definitions.}. Because the SAMURAI dipole cavity (\texttt{vchamber\_box}) extends over $z \in [-1750, +1750]$~mm in yoke-local frame, the target at $z=-919.9$~mm is \emph{physically inside the dipole cavity} rather than upstream of it. Two regions therefore separate the target from the PDCs. \textbf{Region~A} ($\approx 4.3$~m) covers the in-cavity flight from the target through the cavity exit (2.67~m) and onwards through the downstream beam-pipe (\texttt{VacuumDownstream}, $\approx 1.6$~m) up to the Exit Window; this region is controlled by the Geant4 macro switch \texttt{/samurai/geometry/BeamLineVacuum}. \textbf{Region~B} ($\approx 2.0$~m) covers free flight in the world volume from the Exit Window at world $(170.5, 0, 3187.5)$~mm to PDC1 at $(700, 0, 4000)$~mm (0.97~m) and on to PDC2 (1.00~m), gated by \texttt{/samurai/geometry/FillAir}. Inside Region~A the proton bends $\sim 30^\circ$ in the 1.15~T field, but the arc-length vs.\ straight-line difference stays below 10\%\footref{fn:msablation_geom}.

\subsection{Measured \texorpdfstring{$\sigma$}{sigma} values}
Table~\ref{tab:sigma-three-conditions} reproduces the robust half-width $\sigma = (p_{84}-p_{16})/2$ measured at PDC1 and PDC2 across three vacuum/air configurations and three truth momenta, with $|\vec p|=627$~MeV/c protons.

\begin{table}[H]
  \centering
  \small
  \begin{tabular}{lcrrrrrrr}
    \toprule
    Condition & $(p_x, p_y)$ [MeV/c] & $N$ & $\sigma_x$(P1) & $\sigma_y$(P1) & $\sigma_x$(P2) & $\sigma_y$(P2) & $\sigma_{\theta_x}$ & $\sigma_{\theta_y}$ \\
    \midrule
    all\_air         & $(0,0)$    & 50 & 3.071 & 9.736  & 3.669 & 12.826 & 12.279 & 9.240 \\
    all\_air         & $(100,0)$  & 50 & 3.838 & 10.492 & 5.377 & 12.751 & 15.768 & 8.277 \\
    all\_air         & $(0,20)$   & 50 & 3.372 & 13.039 & 4.065 & 14.927 & 21.709 & 7.846 \\
    \midrule
    beamline\_vacuum & $(0,0)$    & 50 & 1.528 & 4.061  & 2.086 & 6.801  & 11.834 & 5.910 \\
    beamline\_vacuum & $(100,0)$  & 50 & 2.067 & 4.888  & 3.060 & 8.211  & 8.100  & 5.786 \\
    beamline\_vacuum & $(0,20)$   & 49 & 1.667 & 4.789  & 2.363 & 7.459  & 14.289 & 5.421 \\
    \midrule
    all\_vacuum      & $(0,0)$    & 50 & 0.147 & 0.515  & 0.447 & 0.947  & 6.798  & 2.558 \\
    all\_vacuum      & $(100,0)$  & 50 & 0.154 & 0.364  & 0.416 & 0.999  & 4.075  & 1.956 \\
    all\_vacuum      & $(0,20)$   & 50 & 0.174 & 0.411  & 0.396 & 1.002  & 6.913  & 2.299 \\
    \bottomrule
  \end{tabular}
  \caption{$\sigma$ values from Geant4 + reconstruction ensemble; $\sigma$ in mm, $\sigma_\theta$ in mrad. Robust half-width $(p_{84}-p_{16})/2$. Source: \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_mixed\_20260422\_zh.md} §4.}
  \label{tab:sigma-three-conditions}
\end{table}

\subsection{Gap to design specifications}
The realistic-air spatial $\sigma_y$(PDC2) sits roughly an order of magnitude away from the 1~mm hardware design figure, and only the all-vacuum ablation reaches the design floor. Table~\ref{tab:design-gap} summarises the comparison; angular and momentum entries follow the same structure.

\begin{table}[H]
  \centering
  \small
  \begin{tabular}{p{4.6cm} p{3.2cm} p{5.2cm} p{2.6cm}}
    \toprule
    Quantity & Design / commissioning & Our current state & Source \\
    \midrule
    Position $\sigma$ at PDC & 1~mm & $\sim 13$~mm (all-air) / $\sim 7.5$~mm (A=vac) / $\sim 1.0$~mm (all-vac) & Kobayashi 2013 §3.4\footref{fn:kobayashi2013} + memo §4\footref{fn:msablation} \\
    Angular $\sigma$ & 2~mrad & 5.4--9.2~mrad ($\sigma_{\theta_y}$, all-air \& \texttt{beamline\_vacuum}) / 2.0--2.6~mrad (all-vacuum) & Kobayashi 2013 §3.4\footref{fn:kobayashi2013} + memo §4\footref{fn:msablation} \\
    RI commissioning $\Delta p / p$ & $1/1500$ & not measured in this ablation & Kobayashi 2013\footref{fn:kobayashi2013} \\
    Proton-mode design $\Delta p / p$ & $\sim 1/700$ & not measured in this ablation & RIBF-TAC05 (2005)\footref{fn:ribftac05} \\
    \bottomrule
  \end{tabular}
  \caption{PDC reconstruction performance: design / commissioning targets vs.\ our current Geant4 + reconstruction state. Position and angular rows compare against the Kobayashi 2013 §3.4 hardware specification; the two $\Delta p/p$ rows are not yet propagated end-to-end in our ablation, so we have $\sigma_y$(PDC2) but no single $\Delta p/p$ figure to report.}
  \label{tab:design-gap}
\end{table}

\subsection{Why this matters for the science floor}
The PDC2 $\sigma_y$ entries above are not the end of the story: they propagate backwards through the Runge--Kutta tracker and the SAMURAI magnetic field map to a target-momentum uncertainty $\sigma_{p,\text{target}}$, which is the reconstruction science floor for any experiment in which the target sits inside the magnet and the outgoing proton is measured downstream (target $\to$ magnet $\to$ PDC). This document does not re-derive $\sigma_{p,\text{target}}$ propagation values; the per-method numerical breakdown lives in the RK error-analysis deep-dive memo\footnote{\label{fn:rkdeepdive}See \texttt{docs/reports/reconstruction/momentum\_reco/rk/rk\_error\_analysis\_deep\_dive\_20260426\_zh.pdf} for $\sigma_{p,\text{target}}$ propagation under MC, Profile, Laplace, MCMC, and MC-PDC.}.

\section{PDC reconstruction reference frame}
% [content from Tasks 4--6]
\subsection{Hardware foundations}
The PDC1/PDC2 hardware specification is documented across four canonical sources: Kobayashi 2013 §3.4\footref{fn:kobayashi2013}, the RIKEN internal \texttt{Detector-PDC.pdf} tech note\footref{fn:detectorpdc}, the SAMURAI 2012 construction proposal\footref{fn:samurai2012}, and the older RIBF-TAC05 (2005) construction proposal\footref{fn:ribftac05}. The proton-arm magnet is the SAMURAI superconducting H-shape dipole described by Sato et al., providing a 7~Tm bending power, a maximum field of 3~T, an 80~cm pole gap and a 2~m pole face, with the field map computed in OPERA-3d / TOSCA\footnote{\label{fn:sato2013}H.~Sato et al., IEEE Trans. Appl. Supercond. \textbf{23}, 4500308 (2013), DOI: \href{https://doi.org/10.1109/TASC.2012.2237225}{10.1109/TASC.2012.2237225}.}. The drift cells follow the Walenta geometry with an 8~mm drift distance, arranged as five planes (U/V/X/U/V) at $\pm 45^\circ/0^\circ$ over a $1700 \times 800$~mm$^2$ active area, filled with Ar + 25\% iC$_4$H$_{10}$ (or alternatively Ar + 50\% C$_2$H$_6$) and read out via $\sim$810 channels\footref{fn:detectorpdc}. The chambers sit at $\sim 59^\circ$ on the proton arm with the design targets of 1~mm position resolution, 2~mrad angular resolution, and 0.8\% relative momentum resolution, with commissioning RI runs reaching $\Delta p/p \approx 1/1500$\footref{fn:kobayashi2013} and a proton-mode design specification of $\Delta p/p \approx 1/700$\footref{fn:ribftac05}. The signal chain feeds an ASD shaper into AMT-VME TDCs at 0.78~ns/ch\footref{fn:ribftac05}, where the AMT chip is the TDC ASIC originally described by Arai\footnote{\label{fn:arai2000}Y.~Arai, Nucl. Instr. Meth. A \textbf{453}, 365 (2000), DOI: \href{https://doi.org/10.1016/S0168-9002(00)00658-6}{10.1016/S0168-9002(00)00658-6}.}. The boundary between the dipole-cavity vacuum (Region~A) and the downstream air volume (Region~B) is the SAMURAI Exit Window, which on the actual SAMURAI spectrometer is a metallic structure; our simulation models it as an iron (G4\_Fe) flange with a Galactic-vacuum or air-filled central aperture (\texttt{libs/smg4lib/src/devices/ExitWindowC1Construction.cc}, \texttt{ExitWindowC2Construction.cc}). The dipole cavity itself is evacuated to a few Pa during operation, as documented for the original 2012 SAMURAI vacuum-system commissioning by Shimizu et al.\footnote{\label{fn:shimizu2013}Y.~Shimizu, H.~Otsu, T.~Kobayashi, T.~Kubo, T.~Motobayashi, H.~Sato, K.~Yoneda, ``Vacuum system for the SAMURAI spectrometer,'' Nucl. Instr. Meth. B \textbf{317}, 739--742 (2013), DOI: \href{https://doi.org/10.1016/j.nimb.2013.08.051}{10.1016/j.nimb.2013.08.051}.}; we cite this reference only for the cavity-evacuated status, not for the exit-window material. The matching offline reconstruction pipeline is the RIKEN ROOT-based drift-chamber analysis described by Otsu et al.\footnote{\label{fn:otsu2016}H.~Otsu et al., Nucl. Instr. Meth. B \textbf{376}, 175 (2016), DOI: \href{https://doi.org/10.1016/j.nimb.2016.02.056}{10.1016/j.nimb.2016.02.056}.}. Together these four canonical sources cover the hardware geometry and design specifications, but none of them publishes a head-to-head proton-arm reconstruction performance paper; that gap is the motivation for §3.2 (algorithm spine) and §3.3 (performance achieved).

\begin{table}[H]
  \centering
  \small
  \begin{tabular}{p{5.0cm} p{5.0cm} p{4.6cm}}
    \toprule
    Item & Value & Source \\
    \midrule
    PDC location              & $\sim 59^\circ$ on proton arm        & Kobayashi 2013 §3.4 \\
    Active area               & $1700 \times 800$~mm$^2$             & Detector-PDC tech note \\
    Drift cell                & Walenta, 8~mm drift                  & Detector-PDC tech note \\
    Plane configuration       & U/V/X/U/V at $\pm 45^\circ/0^\circ$  & Detector-PDC tech note \\
    Primary gas               & Ar + 25\% iC$_4$H$_{10}$             & Detector-PDC tech note \\
    Alternative gas           & Ar + 50\% C$_2$H$_6$                 & Detector-PDC tech note \\
    Channels                  & $\sim 810$                           & Detector-PDC tech note \\
    Readout TDC               & AMT-VME, 0.78~ns/ch                  & RIBF-TAC05 2005 + Arai 2000 \\
    Magnet type               & superconducting H-dipole             & Sato 2013 \\
    Bending power             & 7~Tm                                 & Sato 2013 \\
    Max field                 & 3~T                                  & Sato 2013 \\
    Gap                       & 80~cm                                & Sato 2013 \\
    Pole face                 & 2~m                                  & Sato 2013 \\
    Field map source          & OPERA-3d / TOSCA                     & Sato 2013 \\
    Design position $\sigma$  & 1~mm                                 & Kobayashi 2013 §3.4 \\
    Design angle $\sigma$     & 2~mrad                               & Kobayashi 2013 §3.4 \\
    Design $\Delta p/p$       & 0.8\%                                & Kobayashi 2013 §3.4 \\
    Commissioning RI $\Delta p/p$ & $1/1500$                         & Kobayashi 2013 \\
    Proton mode $\Delta p/p$ design & $\sim 1/700$                   & RIBF-TAC05 2005 \\
    \bottomrule
  \end{tabular}
  \caption{PDC1/PDC2 + magnet + ExitWindow hardware specifications. Sources cited inline; full bibliographic entries in §7.}
  \label{tab:hardware-spec}
\end{table}

\subsection{Algorithm spine}
The published reference reconstruction chain for the SAMURAI proton arm follows a four-stage spine. \textbf{(i)~Hits to track segments.} Drift times measured by the AMT-VME TDCs are converted to drift distances and combined into a straight-line track in each PDC plane; this drift-time-to-distance and per-plane line-fit pipeline is the RIKEN ROOT-based drift-chamber analysis described by Otsu et al.\footref{fn:otsu2016}, deployed within the SAMURAIANA / \texttt{anaroot} framework (cite by repo path \texttt{anaroot/}). \textbf{(ii)~Back-tracking through the magnet.} The PDC-plane track is propagated backwards through the SAMURAI superconducting H-dipole using a Runge--Kutta integrator over the OPERA-3d / TOSCA field map published by Sato et al.\footref{fn:sato2013}; the field map itself is peer-reviewed, but the back-tracking algorithmic recipe is documented only in PhD theses (see point~iii) and not in any peer-reviewed paper. \textbf{(iii)~Optional Kalman smoothing.} A Kalman-filter smoother on the PDC tracks is the standard refinement, but \emph{PDC-side Kalman smoothing has no peer-reviewed publication that we have located.} The closest published paper, Santamaria et al., Nucl. Instr. Meth. A \textbf{905}, 138--148 (2018)\footnote{\label{fn:santamaria2018}C.~Santamaria et al., Nucl. Instr. Meth. A \textbf{905}, 138--148 (2018), DOI: \href{https://doi.org/10.1016/j.nima.2018.07.053}{10.1016/j.nima.2018.07.053}.}, applies a Kalman filter to the MINOS TPC, not the PDCs. We initially expected the PDC-side methodology to live in PhD theses, but an April 2026 web-verification audit of four candidate theses found that none of them contains a PDC reconstruction chapter: Santamaria 2015 (Univ.\ Paris-Saclay)\footnote{\label{fn:santamaria2015phd}C.~Santamaria, PhD thesis, Univ.\ Paris-Saclay (2015), HAL tel-01231191, \url{https://hal.science/tel-01231191}.\ \texttt{[verified 2026-04-27: MINOS TPC vertex tracker only; no PDC content.]}} covers only the MINOS TPC vertex tracker; Kahlbow 2021 (TU Darmstadt)\footnote{\label{fn:kahlbow2019}J.~Kahlbow, PhD thesis, TU Darmstadt (defended 2019; TUprints publication year 2021), TUprints 9192, \url{https://tuprints.ulb.tu-darmstadt.de/9192/}.\ \texttt{[verified 2026-04-27: NeuLAND invariant-mass spectroscopy of $^{29,30}$F; drift-chamber Table~6.1 covers BigRIPS BDC/FDC, not SAMURAI PDC1/PDC2.]}} is a NeuLAND/$^{29,30}$F invariant-mass thesis whose drift-chamber section covers BigRIPS BDC/FDC rather than SAMURAI PDC1/PDC2; Lehr 2022 (TU Darmstadt)\footnote{\label{fn:lehr2023phd}C.~Lehr, PhD thesis, TU Darmstadt (2022), TUprints 20267, \url{https://tuprints.ulb.tu-darmstadt.de/20267/}.\ \texttt{[verified 2026-04-27: BDC/FDC + NEBULA/NeuLAND on the neutron arm; full-text search returns zero hits for ``PDC'', ``PDC1'', ``PDC2''.]}} contains zero PDC mentions and develops a neutron-arm reconstruction algorithm; Storck-Dutine 2023 (TU Darmstadt)\footnote{\label{fn:storck2023phd}S.~Storck-Dutine, PhD thesis, TU Darmstadt (2023), TUprints 23768, \url{https://tuprints.ulb.tu-darmstadt.de/23768/}.\ \texttt{[abstract verified 2026-04-27: $^{26}$O lifetime via fragment--neutron velocity difference, neutron-arm focused; PDF could not be retrieved, no PDC chapter confirmed.]}} is centred on a $^{26}$O lifetime measurement using a fragment--neutron velocity-difference observable on the neutron arm, with PDF retrieval blocked at audit time so PDC content remains unverified rather than confirmed. The honest reading is that we have located \emph{no} public source --- peer-reviewed or PhD --- that documents PDC-side Kalman methodology, and we therefore self-calibrate from internal data (see §4.2). \textbf{(iv)~Output.} The propagated state at the target plane yields the target-frame momentum vector $\vec p_{\text{target}}$ used downstream. As context, several MINOS+SAMURAI groups generate their training and validation data using the NPTool simulation framework of Matta et al., J.\ Phys.\ G \textbf{43}, 045113 (2016)\footnote{\label{fn:matta2016}A.~Matta et al., J.\ Phys.\ G \textbf{43}, 045113 (2016), DOI: \href{https://doi.org/10.1088/0954-3899/43/4/045113}{10.1088/0954-3899/43/4/045113}.}, but NPTool is a simulation framework, not the reconstruction path itself.

Our internal pipeline lives in \texttt{libs/analysis\_pdc\_reco/} (see also \texttt{smsimulator5.5/CLAUDE.md} for the repo-level guide) and follows the same Runge--Kutta back-tracking spine, with multiple selectable RK fit modes; one concrete example is \texttt{-{}-rk-fit-mode fixed-target-pdc-only} as exercised in the MS ablation memo\footref{fn:msablation} §3. An alternative neural-network backend is provided under \texttt{scripts/reconstruction/nn\_target\_momentum/}, and an RK geometry filter (\texttt{libs/qmd\_geo\_filter/}, with the matching skill \texttt{skills/smsim-rk-geometry-filter/}) prunes obviously off-acceptance trajectories before the fit. We do not re-derive the per-method numerical performance here: the full status, including MC, Profile, Laplace, MCMC, and MC-PDC variants, is reported in the RK status memo at \texttt{docs/reports/reconstruction/momentum\_reco/rk/rk\_reconstruction\_status\_20260416\_zh.pdf} and the deep-dive\footref{fn:rkdeepdive}. A detailed algorithm-by-algorithm comparison between the literature spine and our internal pipeline is deferred to §4.2 (Methodology gap).

\subsection{Performance achieved across SAMURAI campaigns}
Table~\ref{tab:performance-campaigns} surveys the public SAMURAI papers that have used the PDC1/PDC2 chain and asks a single question: did the publication report a PDC-side $\sigma_p/p$ figure that we can directly compare against our reconstruction? The answer for almost every entry is no --- public papers report physics observables (cross sections, decay energies, momentum distributions) rather than the upstream tracker resolution. Cells are therefore explicitly marked ``not reported'' or ``needs verification''; we deliberately do not invent numbers.

\begin{table}[H]
  \centering
  \footnotesize
  \begin{tabular}{p{3.0cm} p{1.0cm} p{1.7cm} p{4.4cm} p{1.7cm} p{2.6cm}}
    \toprule
    Experiment & Year & Channel & $\sigma_p/p$ reported & Source flag & Citation \\
    \midrule
    Commissioning RI       & 2012 & RI ions       & $\sim 1/1500$                                              & reported            & Kobayashi 2013\footref{fn:kobayashi2013} \\
    SEASTAR-III $^{28}$O   & 2017 & (p,2p)/(p,pn) & not reported (0.2~MeV FWHM at 0.5~MeV decay-E\footref{fn:codex_2026_04_28} $\leftrightarrow$ inferred $\sim 1\%$) & inferred & Kondo Nature 620 (2023)\footref{fn:kondo2023} \\
    $^{52}$Ca(p,pn)$^{51}$Ca & 2017 & (p,pn)      & not reported                                               & needs verification  & Enciu PRL 129 (2022)\footnote{\label{fn:enciu2022}M.~Enciu et al., Phys. Rev. Lett. \textbf{129}, 262501 (2022), DOI: \href{https://doi.org/10.1103/PhysRevLett.129.262501}{10.1103/PhysRevLett.129.262501}.} \\
    $^{30}$F study         & 2017 & (p,2p)        & not reported                                               & needs verification  & Kahlbow PRL 133 (2024)\footnote{\label{fn:kahlbow2024prl}J.~Kahlbow et al., Phys. Rev. Lett. \textbf{133}, 082501 (2024), DOI: \href{https://doi.org/10.1103/PhysRevLett.133.082501}{10.1103/PhysRevLett.133.082501}.} \\
    $^{50}$Ar(p,pn)$^{49}$Ar & 2017 & (p,pn)      & not reported                                               & needs verification  & Linh PRC 109 (2024)\footnote{\label{fn:linh2024}B.~D.~Linh et al., Phys. Rev. C \textbf{109}, 034312 (2024), DOI: \href{https://doi.org/10.1103/PhysRevC.109.034312}{10.1103/PhysRevC.109.034312}.} \\
    \bottomrule
  \end{tabular}
  \caption{PDC-side $\sigma_p/p$ as reported (or not) in public SAMURAI papers. Cells marked ``needs verification'' or ``inferred'' should not be filled with invented numbers. We have not located any public source --- peer-reviewed or PhD --- that reports a PDC-specific $\sigma_p/p$ figure; the four candidate PhD theses (Kahlbow 2021, Santamaria 2015, Lehr 2022, Storck-Dutine 2023) were verified in April 2026 to cover other detector subsystems (NeuLAND + BigRIPS BDC/FDC, MINOS TPC, neutron-arm reconstruction, $^{26}$O lifetime) rather than the SAMURAI PDC1/PDC2 chain (see §3.2 footnotes).}
  \label{tab:performance-campaigns}
\end{table}

The honest reading of Table~\ref{tab:performance-campaigns} is that almost every public SAMURAI paper reports physics observables (cross sections, decay energies) but not $\sigma_p/p$ directly, so the ``needs verification'' cells are deliberate placeholders for follow-up commits and must never be filled with invented numbers. The Kondo entry is the lone borderline case: the 0.2~MeV FWHM decay-energy resolution lets one \emph{infer} $\sigma_p/p \sim 1\%$ at the order-of-magnitude level, but that figure is inferred and is labelled as such. The remaining ``needs verification'' cells cannot be resolved from any verified public source: the four candidate PhD theses we initially considered (Kahlbow 2021\footref{fn:kahlbow2019}, Santamaria 2015\footref{fn:santamaria2015phd}, Lehr 2022\footref{fn:lehr2023phd}, Storck-Dutine 2023\footref{fn:storck2023phd}) were verified in April 2026 to cover other detector subsystems (see §3.2 for per-thesis verification tags) and contain no PDC reconstruction performance numbers.

\section{Gap analysis}
% [content from Tasks 7--8]
\subsection{Performance: \texorpdfstring{$\sigma$}{sigma} values}
A 2026-04-28 web-verification audit\footnote{\label{fn:codex_2026_04_28}Codex audit 2026-04-28 on four citations used in this document. \textbf{(i)}~Obertelli et al., EPJA \textbf{50}, 8 (2014) abstract describes ``a thick liquid-hydrogen target coupled to a compact TPC serving as a vertex tracker''; the target-outside-magnet / upstream-of-SAMURAI-dipole geometry is \emph{not} stated in the abstract. \textbf{(ii)}~Santamaria et al., NIM A \textbf{905}, 138 (2018) abstract reports MINOS TPC ``vertex position resolution reaches 5~mm FWHM'' and ``overall efficiency better than 90\% for physics experiments''; geometry placement not verifiable from the abstract. \textbf{(iii)}~Kobayashi et al., NIM B \textbf{317}, 294 (2013) accessible text describes BDC1/BDC2 upstream detectors and target--magnet-centre distance 3.9~m but \emph{does not} contain a PDC1/PDC2 position-resolution figure; the often-quoted 1~mm rms PDC2 figure traces to a separate RIKEN SAMURAI PDC detector note (\url{https://nishina.riken.jp/ribf/SAMURAI/image/Detector-PDC.pdf}), a prototype X-ray bench test, not Kobayashi 2013. \textbf{(iv)}~Kondo et al., Nature \textbf{620}, 965 (2023) Methods quote ``a resolution (FWHM) of around 0.2~MeV at 0.5~MeV decay energy'' with parametrised formula $0.14(E+0.87)^{0.81}$~MeV~FWHM; the $\sigma_p/p \sim 1\%$ figure is our order-of-magnitude inference, not stated in the paper.} reassigned the published reference-frame numbers: the often-quoted 1~mm rms position-resolution figure for PDC2 traces to a RIKEN SAMURAI PDC detector note\footnote{\label{fn:riken_pdc_note}RIKEN SAMURAI PDC detector page (PDF): \url{https://nishina.riken.jp/ribf/SAMURAI/image/Detector-PDC.pdf}, ``position resolution of 1~mm (rms) were obtained for x-rays'' on a prototype --- a prototype-bench X-ray number, not an operational fragment-track resolution.} reporting prototype X-ray bench tests, not Kobayashi 2013 §3.4 as initially cited\footref{fn:codex_2026_04_28}; we use it below as a comparison floor only with that caveat. Kobayashi 2013 itself documents the SAMURAI commissioning RI-beam runs reaching $\Delta p/p \approx 1/1500$ at the spectrometer level\footref{fn:kobayashi2013}; the 2~mrad angular and 0.8\% relative-momentum figures formerly attributed to Kobayashi 2013 §3.4 are not verifiable from the accessible text and are dropped here. The most recent public physics-grade comparison point is the SEASTAR-III $^{28}$O measurement of Kondo et al.\footnote{\label{fn:kondo2023}Y.~Kondo et al., Nature \textbf{620}, 965--970 (2023), DOI: \href{https://doi.org/10.1038/s41586-023-06352-6}{10.1038/s41586-023-06352-6}.}, whose Methods report a decay-energy resolution of $\approx 0.2$~MeV FWHM \emph{at $0.5$~MeV decay energy} with parametrised formula $0.14(E+0.87)^{0.81}$~MeV~FWHM\footref{fn:codex_2026_04_28}; propagating that to a PDC-side relative momentum resolution gives $\sigma_p/p \sim 1\%$ at the order-of-magnitude level, but this is our inference (not stated in the Kondo paper) and is flagged as such here.

In our own Geant4 + reconstruction chain, the directly observable spatial spread is $\sigma_y(\text{PDC2}) = 12.83$--$14.93$~mm in the all-air configuration, $6.80$--$8.21$~mm when Region~A (dipole cavity + beam pipe) is set to vacuum (\texttt{beamline\_vacuum}), and approximately $1.0$~mm in the all-vacuum configuration; the corresponding $\sigma_{\theta_y}$ falls in 5.4--9.2~mrad for the all-air and \texttt{beamline\_vacuum} cases and 2.0--2.6~mrad for the all-vacuum case\footref{fn:msablation}. We do not introduce new numbers in this subsection; all entries are reproduced from Table~\ref{tab:sigma-three-conditions} in §2.

The position $\sigma_y$ at PDC2 is therefore an order of magnitude away from the 1~mm RIKEN PDC prototype X-ray bench figure\footref{fn:riken_pdc_note} in both the all-air and the \texttt{beamline\_vacuum} configurations. Only the all-vacuum ablation reaches that bench floor: $\sigma_y(\text{PDC2}) \approx 1.0$~mm matches the prototype-bench number to within the ablation precision. The 2~mrad angular and 0.8\% relative-momentum reference figures originally compared against in this paragraph were attributed to Kobayashi 2013 §3.4 but were not verifiable in the 2026-04-28 audit\footref{fn:codex_2026_04_28} and are dropped from this comparison; the absolute $\sigma_{\theta_y}$ values from our ablation (5.4--9.2~mrad in air/\texttt{beamline\_vacuum}, 2.0--2.6~mrad in all-vacuum) are kept in §2 Table~\ref{tab:sigma-three-conditions} but no longer benchmarked against an unverified design value. We do not yet have an end-to-end $\sigma_p/p$ figure from this ablation; the per-method $\sigma_{p,\text{target}}$ propagation methodology under MC, Profile, Laplace, MCMC, and MC-PDC is documented in the RK error-analysis deep-dive memo\footref{fn:rkdeepdive} and is not re-derived here.

The interpretation of this gap structure matters for how follow-up work is scoped. The fact that the all-vacuum ablation lands on the 1~mm prototype-bench floor\footref{fn:riken_pdc_note} is direct evidence that the reconstruction methodology itself is sound: the same RK back-tracking + drift-chamber pipeline that produces the 13~mm number in air produces the 1~mm number in vacuum, with no algorithmic change between the two. The gap to that bench reference is therefore primarily a material-budget problem rather than a methodology problem, and the responsibility for closing it sits with §4.3 (material budget and vacuum configuration). The $\sigma_y$(PDC2) entries propagate backwards through the RK tracker and the SAMURAI field map to a target-momentum uncertainty $\sigma_{p,\text{target}}$, and that propagation is captured method-by-method in the RK deep-dive\footref{fn:rkdeepdive}.

\subsection{Methodology}
The published methodology spine for the SAMURAI proton arm has three pieces. RK back-tracking through the Sato 2013 OPERA-3d / TOSCA field map\footref{fn:sato2013} forms the propagator; the front-end drift-chamber pipeline (drift-time-to-distance, per-plane line fit) is the RIKEN ROOT-based analysis of Otsu et al.\footref{fn:otsu2016}; an optional Kalman smoother on the PDC tracks is the standard refinement step but has \emph{no peer-reviewed paper covering the PDC-side methodology}. The closest published Kalman paper is Santamaria et al.\ Nucl. Instr. Meth. A \textbf{905} (2018)\footref{fn:santamaria2018}, which applies a Kalman filter to the MINOS TPC rather than the PDCs. We initially expected the PDC-side methodology to live in PhD theses, but the April 2026 verification documented in §3.2 found that none of the four candidate theses (Santamaria 2015\footref{fn:santamaria2015phd}, Kahlbow 2021\footref{fn:kahlbow2019}, Lehr 2022\footref{fn:lehr2023phd}, Storck-Dutine 2023\footref{fn:storck2023phd}) contains a PDC reconstruction chapter; we therefore have \emph{no} verified public source for the PDC-side Kalman methodology.

Our internal pipeline lives in \texttt{libs/analysis\_pdc\_reco/} (with the repo-level guide in \texttt{smsimulator5.5/CLAUDE.md}) and matches the literature spine piece-for-piece: it provides the same RK back-tracking propagator, exposes multiple selectable RK fit modes (one concrete example being \texttt{-{}-rk-fit-mode fixed-target-pdc-only} as exercised in the MS ablation memo\footref{fn:msablation}), wraps a neural-network backend under \texttt{scripts/reconstruction/nn\_target\_momentum/}, and runs a geometry filter (\texttt{libs/qmd\_geo\_filter/}) before the fit. The full numerical status of the RK pipeline, including MC, Profile, Laplace, MCMC, and MC-PDC variants, is recorded in the RK status memo\footnote{\label{fn:rkstatus}See \texttt{docs/reports/reconstruction/momentum\_reco/rk/rk\_reconstruction\_status\_20260416\_zh.pdf} for the per-method RK reconstruction status.} and the deep-dive\footref{fn:rkdeepdive}.

The methodological gap to the published reference frame is therefore small in algorithm shape: literature and our pipeline use the same RK back-tracking and the same optional Kalman smoothing. The \emph{actionable} gap is process-noise calibration. The Santamaria 2018 NIM A paper\footref{fn:santamaria2018} (which is MINOS TPC, not PDC) does not publish a process-noise covariance tuned to a magnet + air configuration, and the four PhD theses listed in §3.2 do not cover PDC reconstruction at all (verified April 2026); there is no public table that maps a given dipole + cavity + beam-pipe + downstream-air configuration to a Kalman process-noise covariance one can drop into our smoother. The quadrature decomposition in the MS ablation memo\footref{fn:msablation} §6 (with $\sigma_A \approx 11.19$~mm from Region~A and $\sigma_B \approx 7.43$~mm from Region~B) is exactly the per-region calibration data needed to set process-noise inputs for our specific geometry, and it does not exist in the public literature for this configuration.

The interpretation is that the published reference frame supplies the methodology shape (RK + optional Kalman), but it does not supply the configuration-specific tuning numbers, so we have to self-calibrate the process-noise inputs against our own ablation data rather than read them off a literature table. This is a closeable gap rather than a fundamental obstacle: the calibration data already exists internally\footref{fn:msablation}, and feeding it into the Kalman smoother is the next concrete methodology step.
\subsection{Material budget and vacuum configuration}
The published reference frame for the SAMURAI vacuum system is Shimizu et al.\ Nucl. Instr. Meth. B \textbf{317}, 739--742 (2013)\footref{fn:shimizu2013}, which documents the dipole cavity as evacuated to a few Pa during the original 2012 commissioning. (We deliberately do not cite this paper for exit-window material: the actual SAMURAI exit window is metallic, and we treat that as a domain fact rather than a paper-derived claim here.) Whether the SEASTAR-III / SAMURAI21 (2017) campaign in particular kept this evacuated-cavity configuration is \emph{inferred from Shimizu 2013 plus standard SAMURAI21 operation}; we do not have a direct quote in the surveyed references that explicitly confirms the Region~A vacuum status for SAMURAI21 (2017), and the claim is flagged as inferred rather than quoted.

In our own Geant4 setup, the Region~A vacuum status is under exploration rather than fixed. Two candidates from the MS ablation memo\footref{fn:msablation} §6 frame the choice numerically: with Region~A set to vacuum the stage~D PDC2 spread is $\sigma_y(\text{PDC2}) = 7.49$~mm, and with Region~A set to air it rises to $\sigma_y(\text{PDC2}) = 13.50$~mm. Both candidates are documented and neither is asserted to be the actual experimental run condition.

If the literature default is the evacuated cavity (inferred) and our $\sigma_y$ under that configuration is 7.49~mm, the residual gap to the 1~mm hardware design figure is dominated by Region~B (Exit Window $\to$ PDCs, $\approx 2$~m of air); if instead our actual configuration is an air-filled cavity giving 13.50~mm, the gap is dominated by Region~A. The quadrature decomposition in the same memo\footref{fn:msablation} §5.2 gives $\sigma_A \approx 11.19$~mm from Region~A and $\sigma_B \approx 7.43$~mm from Region~B, so Region~A air vs.\ vacuum is the single most consequential configuration question for closing the $\sigma$ gap.

Per the project's discipline on experimental-reality claims, we deliberately do not assert which of the two Region~A configurations corresponds to the actual experimental run; documenting both 7.49~mm and 13.50~mm candidates is the honest position. The actionable next step is collaborator confirmation of the SAMURAI21 (2017) Region~A status --- this is an engineering / operational question rather than a physics one, and it should be settled by reading the run-time vacuum logs or by direct contact with the SAMURAI operations group rather than by simulation alone.

\subsection{Experimental configuration and geometry}
The published reference frame for the SAMURAI + MINOS terminal places the reaction target outside the dipole magnet (operationally documented across the SEASTAR-II/III publications, but \emph{not} a primary claim of either Obertelli 2014 or Santamaria 2018 abstracts when audited\footref{fn:codex_2026_04_28}): the MINOS programme of Obertelli et al., EPJA \textbf{50}, 8 (2014)\footnote{\label{fn:obertelli2014}A.~Obertelli et al., Eur. Phys. J. A \textbf{50}, 8 (2014), DOI: \href{https://doi.org/10.1140/epja/i2014-14008-y}{10.1140/epja/i2014-14008-y}.} introduces a thick LH$_2$ target coupled to a compact TPC vertex tracker, with a typical SEASTAR beam energy of $\sim 250$~MeV/u; the implementation paper of Santamaria et al.\ NIM~A \textbf{905}, 138--148 (2018)\footref{fn:santamaria2018} documents the MINOS TPC tracking and reports vertex-position resolution $\approx 5$~mm FWHM with overall efficiency $> 90\%$\footref{fn:codex_2026_04_28}.

In our setup, the deuteron target sits at world coordinates $(-12.488, 0.0009, -1069.458)$~mm and is therefore physically inside the SAMURAI dipole cavity rather than upstream of it\footref{fn:msablation_geom}. The proton kinematics is fixed at $|\vec p| = 627$~MeV/c, corresponding to $\sim 190$~MeV/u kinetic energy\footref{fn:msablation}; there is no vertex detector around the target.

Region~B ($\sim 2.0$~m, Exit Window $\to$ PDCs) is \emph{directly comparable} to the literature in dipole and PDC1/PDC2 hardware specification, but no verified public source provides a PDC-side $\sigma_p/p$ figure to benchmark against (see §3.2). Region~A ($\sim 4.3$~m, target-inside-cavity flight) has \emph{no literature precedent}: published SAMURAI+MINOS configurations all place the target outside the magnet, so the in-cavity 4.3~m flight path is a configuration unique to our experiment.

The interpretation is that the geometry difference between literature and our experiment is by design --- our experiment puts the target inside the dipole cavity for physics reasons, while MINOS puts it outside for vertex-tracking reasons --- and is therefore not actionable in the sense that we should change the geometry to chase a literature number. What it does explain is why no published $\sigma_p/p$ figure applies to our setup directly: every public benchmark is for a target-outside-magnet configuration, and ours is the first target-inside-magnet case for this PDC chain. Even Region~B, which matches the literature hardware most closely, has no verified public PDC-side $\sigma_p/p$ benchmark (see §3.2 audit), so both Region~A and Region~B must be self-calibrated against our own ablation data.

\begin{table}[H]
  \centering
  \small
  \begin{tabularx}{\linewidth}{l X X X}
    \toprule
    Axis & Literature reference & Our state & Action item \\
    \midrule
    Performance $\sigma_y$ at PDC2 & 1~mm rms prototype X-ray (RIKEN PDC note\footref{fn:riken_pdc_note}); no operational PDC-side $\sigma_p/p$ verified\footref{fn:codex_2026_04_28} & $\sim 13$~mm all-air / $\sim 7.5$~mm A=vac (ms\_ablation §4) & Region~A vacuum decision \\
    Methodology & RK + optional Kalman; no verified public source (4-thesis audit returned zero PDC chapters, §3.2) & \texttt{libs/analysis\_pdc\_reco/} & Self-calibrate process-noise from ms\_ablation §6 \\
    Material budget / vacuum & Cavity evacuated, standard SAMURAI (Shimizu 2013) & Region~A status under exploration (ms\_ablation §6) & Confirm SAMURAI21 (2017) Region~A config from collaborators \\
    Geometry & Target outside magnet, MINOS+TPC (Obertelli 2014) & Target inside cavity, no vertex (ms\_ablation §1.1) & None --- by-design difference \\
    \bottomrule
  \end{tabularx}
  \caption{Four-axis gap matrix between SAMURAI PDC reconstruction literature and our current state.}
  \label{tab:gap-matrix}
\end{table}

\section{Broader MINOS+SEASTAR chain context}
This section provides bibliographic context only; it does not change the gap analysis in §4.

\subsection{SEASTAR programme timeline}
The SEASTAR (``Shell Evolution And Search for Two-plus energies At the RIBF'') programme had two distinct hardware phases. The first phase, SEASTAR-I and SEASTAR-II, ran on the F8 / ZeroDegree spectrometer and produced the discovery papers on $^{78}$Ni-region structure: Santamaria et al., Phys. Rev. Lett. \textbf{115}, 192501 (2015)\footnote{\label{fn:santamaria2015prl}C.~Santamaria et al., Phys. Rev. Lett. \textbf{115}, 192501 (2015), DOI: \href{https://doi.org/10.1103/PhysRevLett.115.192501}{10.1103/PhysRevLett.115.192501}.}, Doornenbal et al., Phys. Rev. C \textbf{95}, 041301 (2017)\footnote{\label{fn:doornenbal2017}P.~Doornenbal et al., Phys. Rev. C \textbf{95}, 041301 (2017), DOI: \href{https://doi.org/10.1103/PhysRevC.95.041301}{10.1103/PhysRevC.95.041301}.}, and Taniuchi et al., Nature \textbf{569}, 53 (2019)\footnote{\label{fn:taniuchi2019}R.~Taniuchi et al., Nature \textbf{569}, 53 (2019), DOI: \href{https://doi.org/10.1038/s41586-019-1155-x}{10.1038/s41586-019-1155-x}.}.

The second phase, from approximately 2017 onward, moved the MINOS target into the SAMURAI cave and used the proton arm with the PDC1/PDC2 chain. Representative publications include Cortés et al., Phys. Lett. B \textbf{800}, 135071 (2020)\footnote{\label{fn:cortes2020}M.~L.~Cortés et al., Phys. Lett. B \textbf{800}, 135071 (2020), DOI: \href{https://doi.org/10.1016/j.physletb.2019.135071}{10.1016/j.physletb.2019.135071}.}, Kondo et al., Nature \textbf{620} (2023)\footnote{\label{fn:kondo2023ref}Y.~Kondo et al., Nature \textbf{620}, 965--970 (2023), DOI: \href{https://doi.org/10.1038/s41586-023-06352-6}{10.1038/s41586-023-06352-6}. (Same as Table~\ref{tab:performance-campaigns}.)}, and Kahlbow et al., Phys. Rev. Lett. \textbf{133}, 082501 (2024)\footnote{\label{fn:kahlbow2024prlref}J.~Kahlbow et al., Phys. Rev. Lett. \textbf{133}, 082501 (2024), DOI: \href{https://doi.org/10.1103/PhysRevLett.133.082501}{10.1103/PhysRevLett.133.082501}.}. The F8/ZeroDegree campaigns ran before SAMURAI received its proton arm; only the F13/SAMURAI campaigns from $\sim$2017 onward use the PDC1/PDC2 chain.

\subsection{Companion detectors}
The PDC1/PDC2 chain co-exists with several other detectors in the SAMURAI cave. Each item below is a one-line role + a citation; this is not an exhaustive sub-system review.
\begin{itemize}
  \item \textbf{MINOS} --- liquid hydrogen vertex tracker with TPC, target sits outside the magnet; co-exists with PDC1/PDC2 in the SAMURAI proton arm. A.~Obertelli et al., Eur. Phys. J. A \textbf{50}, 8 (2014)\footref{fn:obertelli2014}.
  \item \textbf{NeuLAND} --- large-area neutron time-of-flight array; co-exists with PDC1/PDC2 in the SAMURAI proton arm. K.~Boretzky et al., Nucl. Instr. Meth. A \textbf{1014}, 165701 (2021)\footnote{\label{fn:boretzky2021}K.~Boretzky et al., Nucl. Instr. Meth. A \textbf{1014}, 165701 (2021), DOI: \href{https://doi.org/10.1016/j.nima.2021.165701}{10.1016/j.nima.2021.165701}.}.
  \item \textbf{NEBULA} --- plastic-scintillator neutron detector at SAMURAI; co-exists with PDC1/PDC2 in the SAMURAI proton arm. The cross-cutting reference is the SAMURAI/NEBULA recent-developments paper by Kondo, Tomai, Nakamura, Nucl. Instr. Meth. B \textbf{463}, 173--178 (2020)\footnote{\label{fn:kondo2020nim}Y.~Kondo, T.~Tomai, T.~Nakamura, ``Recent progress and developments for experimental studies with the SAMURAI spectrometer,'' Nucl. Instr. Meth. B \textbf{463}, 173--178 (2020), DOI: \href{https://doi.org/10.1016/j.nimb.2019.05.068}{10.1016/j.nimb.2019.05.068}.}.
  \item \textbf{DALI2+} --- NaI(Tl) $\gamma$-ray array; co-exists with PDC1/PDC2 in the SAMURAI proton arm. S.~Takeuchi et al., Nucl. Instr. Meth. A \textbf{763}, 596 (2014)\footnote{\label{fn:takeuchi2014}S.~Takeuchi et al., Nucl. Instr. Meth. A \textbf{763}, 596 (2014), DOI: \href{https://doi.org/10.1016/j.nima.2014.06.087}{10.1016/j.nima.2014.06.087}.}.
  \item \textbf{HODP} --- hodoscope plastic for forward charged-fragment identification; co-exists with PDC1/PDC2 in the SAMURAI proton arm. No dedicated NIM publication identified --- described in Kobayashi 2013 §3.4\footref{fn:kobayashi2013}.
  \item \textbf{CATANA} --- Si+CsI charged-particle array; co-exists with PDC1/PDC2 in the SAMURAI proton arm. CATANA NIM publication not located in this survey --- described in Kondo et al., Nature \textbf{620} (2023) supplementary material\footref{fn:kondo2023ref}.
  \item \textbf{STRASSE} --- next-generation CH$_2$ silicon-strip target tracker, in development; co-exists with PDC1/PDC2 in the SAMURAI proton arm. H.~N.~Liu et al., Eur. Phys. J. A \textbf{59}, 125 (2023)\footnote{\label{fn:liu2023}H.~N.~Liu et al., Eur. Phys. J. A \textbf{59}, 125 (2023), DOI: \href{https://doi.org/10.1140/epja/s10050-023-01023-6}{10.1140/epja/s10050-023-01023-6}.}.
\end{itemize}

\subsection{Reviews and resources}
Two review articles cover the broader methodology. T.~Aumann, Prog. Part. Nucl. Phys. \textbf{118}, 103847 (2021)\footnote{\label{fn:aumann2021}T.~Aumann, Prog. Part. Nucl. Phys. \textbf{118}, 103847 (2021), DOI: \href{https://doi.org/10.1016/j.ppnp.2021.103847}{10.1016/j.ppnp.2021.103847}.} reviews nuclear reactions with radioactive beams and covers SAMURAI campaigns. V.~Panin, T.~Aumann, C.~A.~Bertulani, Eur. Phys. J. A \textbf{57}, 103 (2021)\footnote{\label{fn:panin2021}V.~Panin, T.~Aumann, C.~A.~Bertulani, ``Quasi-free scattering in inverse kinematics as a tool to unveil the structure of nuclei,'' Eur. Phys. J. A \textbf{57}, 103 (2021), DOI: \href{https://doi.org/10.1140/epja/s10050-021-00416-9}{10.1140/epja/s10050-021-00416-9}.} reviews quasi-free scattering in inverse kinematics, the methodological frame for MINOS+SAMURAI.

A 2024 series of arXiv preprints submitted to PTEP covers direct reactions with hydrogen targets at the RIBF, including: K.~Yoshida and J.~Tanaka, ``Reaction mechanism of quasi-free knockout processes in exotic RI beam era,'' arXiv:2412.16649\footnote{\label{fn:yoshida2024}K.~Yoshida and J.~Tanaka, \href{https://arxiv.org/abs/2412.16649}{arXiv:2412.16649} (submitted to PTEP).}; J.~Kahlbow, ``The southern shore of the island of inversion studied via quasi-free scattering,'' arXiv:2412.16799\footnote{\label{fn:kahlbow2024arxiv}J.~Kahlbow, \href{https://arxiv.org/abs/2412.16799}{arXiv:2412.16799} (submitted to PTEP).}; R.~Taniuchi, ``Competition of the shell closure and deformations across the doubly magic $^{78}$Ni,'' arXiv:2412.16972\footnote{\label{fn:taniuchi2024}R.~Taniuchi, \href{https://arxiv.org/abs/2412.16972}{arXiv:2412.16972} (submitted to PTEP).}; and J.~Tanaka, M.~L.~Cortés, H.~Liu, R.~Taniuchi, ``Detectors for next-generation quasi-free scattering experiments at the RIBF,'' arXiv:2412.17887\footnote{\label{fn:tanaka2024}J.~Tanaka, M.~L.~Cortés, H.~Liu, R.~Taniuchi, \href{https://arxiv.org/abs/2412.17887}{arXiv:2412.17887} (submitted to PTEP).}. The RIKEN Accelerator Progress Report archive\footnote{\label{fn:rikenapr}RIKEN Nishina Center, \emph{RIKEN Accelerator Progress Report} archive, \url{https://nishina.riken.jp/researcher/APR/index_e.html}.} contains annual reports including PDC commissioning notes from 2012 onward.

\subsection{Caveats from the broader bibliography}
``PDC'' is RIKEN-internal terminology; most published papers refer to the device as ``drift chambers downstream of the SAMURAI magnet'' rather than PDC1/PDC2, which complicates literature search. Several papers that look like SAMURAI PDC results on first reading must be excluded from the gap analysis: Kubota et al., Phys. Rev. Lett. \textbf{125}, 252501 (2020)\footnote{\label{fn:kubota2020}Y.~Kubota et al., Phys. Rev. Lett. \textbf{125}, 252501 (2020), DOI: \href{https://doi.org/10.1103/PhysRevLett.125.252501}{10.1103/PhysRevLett.125.252501}.} uses the dedicated RPD (recoil proton detector), not PDC; Tanaka et al., Science \textbf{371}, 260 (2021)\footnote{\label{fn:tanaka2021}J.~Tanaka et al., Science \textbf{371}, 260 (2021), DOI: \href{https://doi.org/10.1126/science.abe4688}{10.1126/science.abe4688}.} was performed at RCNP, not SAMURAI; and SEASTAR-I/II at F8/ZeroDegree predates the SAMURAI proton arm and does not use PDC1/PDC2.

\section{Implications and next steps}
% [content from Task 10]
\subsection{Short-term data acquisition action items}
The following items are candidate next steps for closing literature-side data gaps; they are scoped to bibliographic retrieval and collaborator queries rather than to new simulations.
\begin{itemize}
  \item \textbf{Search grey literature beyond the four already-audited PhD theses} for any document that reports a PDC-specific $\sigma_p/p$, drift-time-to-distance calibration, or Kalman process-noise covariance. The April 2026 audit (§3.2) confirmed that Kahlbow 2021, Santamaria 2015, Lehr 2022 (TUprints 20267), and Storck-Dutine 2023 do \emph{not} contain such a chapter; promising next sources include the RIKEN APR archive (next item), conference proceedings of SAMURAI users, and direct contact with the SAMURAI operations group. The goal is to fill the ``needs verification'' cells in Table~\ref{tab:performance-campaigns} (§3.3) only with sourced numbers, never with placeholders or invented values.
  \item \textbf{Browse the RIKEN Accelerator Progress Report (APR) archive} for volumes 46--58 (\url{https://nishina.riken.jp/researcher/APR/index_e.html})\footref{fn:rikenapr} and search for entries by V.~Panin, M.~Kurokawa, and H.~Otsu mentioning PDC commissioning notes. Candidate next step --- short bibliographic notes here can plausibly resolve several ``needs verification'' cells without recourse to a full PhD-length document.
  \item \textbf{Confirm the SAMURAI21 (2017) Region~A vacuum configuration} from collaborators or internal run-time records. If confirmed, this closes the open question identified in §4.3 paragraph 4 about whether the literature-default cavity-evacuated configuration matches the SAMURAI21 run; until then, the air-vs-vacuum status remains an open question and both candidates ($\sigma_y(\text{PDC2}) = 7.49$~mm and $13.50$~mm) should continue to be documented side by side.
\end{itemize}

\subsection{Medium-term simulation and analysis directions}
The following items are conditional on the outcome of §6.1 and on the broader RK status; they are explicitly framed as ``if confirmed'' rather than as commitments.
\begin{itemize}
  \item \textbf{Region~A vacuum engineering feasibility.} If a future run configures Region~A as vacuum, an engineering-feasibility assessment (vacuum interlocks, cavity pumping, beam-pipe connection to the dipole cavity) becomes the corresponding action item from the gap matrix in Table~\ref{tab:gap-matrix}. This step is contingent on the §6.1 collaborator confirmation and is not pursued speculatively.
  \item \textbf{Run \texttt{ms\_ablation} stage~D} feeding $\sigma_A \approx 11.19$~mm and $\sigma_B \approx 7.43$~mm (per\footref{fn:msablation} §6) as RK process-noise inputs. The goal is to complete the methodology-gap closure identified in §4.2 paragraph~3, where the actionable gap is configuration-specific process-noise calibration rather than algorithm shape.
  \item \textbf{Compare the resulting $\sigma_{p,\text{target}}$ against the literature $\sim 1\%$ figure} once stage~D propagates $\sigma_A$ and $\sigma_B$ back through the RK tracker and the SAMURAI field map. The reference point is the Kondo 2023 SEASTAR-III decay-energy resolution, from which $\sigma_p/p \sim 1\%$ is inferred at the order-of-magnitude level\footref{fn:kondo2023ref}. The current $\sigma_{p,\text{target}}$ propagation methodology is documented in the RK error-analysis deep-dive\footref{fn:rkdeepdive}, with the broader RK status in\footref{fn:rkstatus}.
\end{itemize}

\subsection{Open questions}
The following items are deliberately phrased as questions; none of them is closed by the current document.
\begin{itemize}
  \item \textbf{Is the actual SAMURAI21 (2017) Region~A air or vacuum?} This is under exploration. Both candidates are documented numerically: $\sigma_y(\text{PDC2}) = 7.49$~mm if Region~A is vacuum, and $\sigma_y(\text{PDC2}) = 13.50$~mm if both Region~A and Region~B are air (per\footref{fn:msablation} §6). See §4.3 for the configuration discussion.
  \item \textbf{Is our PDC alignment consistent with the literature standard?} No PDC alignment data or alignment-comparison study has been produced internally to date; this is a follow-up question rather than a settled point, and a literature-vs-our-state alignment comparison has not been attempted in this document.
  \item \textbf{What is the source of our drift-time-to-distance calibration --- simulated or measured?} The calibration is currently consumed via the \texttt{libs/analysis\_pdc\_reco/} defaults; the provenance (simulated vs.\ measured) should be verified before any numerical drift-distance accuracy figure is quoted. The April 2026 audit (§3.2) found no public PDC-side calibration reference that we could directly compare against, so this remains an open internal question rather than a literature-comparison exercise.
\end{itemize}

\subsection{Non-goals}
This document deliberately excludes several scopes to keep its boundary tight. It does \emph{not} re-run any \texttt{ms\_ablation} simulations; it does \emph{not} modify the RK reconstruction code; it does \emph{not} commit to a Region~A vacuum decision (both 7.49~mm and 13.50~mm candidates are documented honestly side by side); and it does \emph{not} derive new $\sigma_{p,\text{target}}$ propagation values --- those live in the RK error-analysis deep-dive memo\footref{fn:rkdeepdive}. These are deliberate non-goals, not oversights.

\section{References}
This section is the bibliography for this document. Every entry below carries either a DOI, an arXiv identifier, a thesis-repository handle (TUprints / HAL), or a full URL. Entries whose DOIs were not independently verified at the time of writing are marked \texttt{[DOI not verified]}. Flag tags such as \texttt{[F13/PDC]}, \texttt{[F8-ZDS]}, \texttt{[exclude]}, \texttt{[F13/PDC, confirmed]}, \texttt{[F13/PDC, implicit]}, \texttt{[F13/PDC, expected]}, \texttt{[partial]} indicate the SAMURAI focal-plane configuration and the strength of the PDC linkage for each entry; they follow the convention used throughout this document.

\subsection{Hardware and methodology (peer-reviewed, foundational)}
\begin{itemize}
  \item Kobayashi T., et al., ``SAMURAI spectrometer for RI beam experiments,'' Nucl.\ Instrum.\ Methods B \textbf{317}, 294--304 (2013), DOI: \href{https://doi.org/10.1016/j.nimb.2013.05.089}{10.1016/j.nimb.2013.05.089}. \texttt{[F13/PDC]}
  \item Sato H., et al., ``Superconducting Dipole Magnet for SAMURAI Spectrometer,'' IEEE Trans.\ Appl.\ Supercond.\ \textbf{23}, 4500308 (2013), DOI: \href{https://doi.org/10.1109/TASC.2012.2237225}{10.1109/TASC.2012.2237225}.
  \item Shimizu Y., Otsu H., Kobayashi T., Kubo T., Motobayashi T., Sato H., Yoneda K., ``Vacuum system for the SAMURAI spectrometer,'' Nucl.\ Instrum.\ Methods B \textbf{317}, 739--742 (2013), DOI: \href{https://doi.org/10.1016/j.nimb.2013.08.051}{10.1016/j.nimb.2013.08.051}. \texttt{[cite for cavity-evacuated status only; not for exit-window material]}
  \item Otsu H., et al., ``SAMURAI in its operation phase for RIBF users,'' Nucl.\ Instrum.\ Methods B \textbf{376}, 175 (2016), DOI: \href{https://doi.org/10.1016/j.nimb.2016.02.056}{10.1016/j.nimb.2016.02.056}.
  \item Nakamura T.\ and Kondo Y., review, Nucl.\ Instrum.\ Methods B \textbf{376}, 156 (2016), \href{https://arxiv.org/abs/1512.08380}{arXiv:1512.08380}.
  \item Arai Y., et al., Nucl.\ Instrum.\ Methods A \textbf{453}, 365 (2000), DOI: \href{https://doi.org/10.1016/S0168-9002(00)00658-6}{10.1016/S0168-9002(00)00658-6}.
\end{itemize}

\subsection{Algorithm references}
\begin{itemize}
  \item Santamaria C., et al., ``Tracking with the MINOS TPC,'' Nucl.\ Instrum.\ Methods A \textbf{905}, 138--148 (2018), DOI: \href{https://doi.org/10.1016/j.nima.2018.07.053}{10.1016/j.nima.2018.07.053}.
  \item Matta A., et al., ``NPTool,'' J.\ Phys.\ G \textbf{43}, 045113 (2016), DOI: \href{https://doi.org/10.1088/0954-3899/43/4/045113}{10.1088/0954-3899/43/4/045113}.
  \item Panin V., et al., Phys.\ Lett.\ B \textbf{753}, 204--210 (2016), DOI: \href{https://doi.org/10.1016/j.physletb.2015.11.082}{10.1016/j.physletb.2015.11.082}. \texttt{[R3B/LAND, methodological precursor]}
\end{itemize}

\subsection{PhD theses checked (none contain PDC reconstruction methodology)}
The four theses below were initially considered as candidate PDC-side reconstruction sources. An April 2026 web-verification audit (results inline in §3.2 footnote tags) found that none of them contains a PDC1/PDC2 reconstruction chapter. They are listed here to document the search, not as PDC sources.
\begin{itemize}
  \item Kahlbow J.\ (2021), TU Darmstadt, TUprints 9192, \url{https://tuprints.ulb.tu-darmstadt.de/9192/}. \texttt{[verified 2026-04-27: NeuLAND invariant-mass spectroscopy of $^{29,30}$F; drift-chamber Table~6.1 covers BigRIPS BDC/FDC, not SAMURAI PDC1/PDC2.]}
  \item Santamaria C.\ (2015), Univ.\ Paris-Saclay, HAL tel-01231191, \url{https://hal.science/tel-01231191}. \texttt{[verified 2026-04-27: MINOS TPC vertex tracker only; no PDC content.]}
  \item Lehr C.\ (2022), TU Darmstadt, TUprints 20267, \url{https://tuprints.ulb.tu-darmstadt.de/20267/}. \texttt{[verified 2026-04-27: BDC/FDC + NEBULA/NeuLAND on the neutron arm; full-text search returns zero hits for ``PDC'', ``PDC1'', ``PDC2''.]}
  \item Storck-Dutine S.\ (2023), TU Darmstadt, TUprints 23768, \url{https://tuprints.ulb.tu-darmstadt.de/23768/}. \texttt{[abstract verified 2026-04-27: $^{26}$O lifetime via fragment--neutron velocity difference, neutron-arm focused; PDF retrieval blocked at audit time, no PDC chapter confirmed.]}
\end{itemize}
The following theses were excluded earlier on subject-area grounds and were not part of the April 2026 audit:
\begin{itemize}
  \item Panin V.\ (2012), TUprints 3170. \texttt{[excluded --- R3B/LAND]}
  \item Atar L.\ (2015), GSI-2016-00315. \texttt{[excluded --- R3B/LAND]}
\end{itemize}

\subsection{Physics papers using PDC1/PDC2 (confirmed/implicit)}
\begin{itemize}
  \item Kondo Y., et al., Nature \textbf{620}, 965--970 (2023), DOI: \href{https://doi.org/10.1038/s41586-023-06352-6}{10.1038/s41586-023-06352-6}. \texttt{[F13/PDC, implicit]}
  \item Kahlbow J., et al., Phys.\ Rev.\ Lett.\ \textbf{133}, 082501 (2024), DOI: \href{https://doi.org/10.1103/PhysRevLett.133.082501}{10.1103/PhysRevLett.133.082501}. \texttt{[F13/PDC]}
  \item Revel A., et al., Phys.\ Rev.\ Lett.\ \textbf{124}, 152502 (2020), DOI: \href{https://doi.org/10.1103/PhysRevLett.124.152502}{10.1103/PhysRevLett.124.152502}. \texttt{[F13/PDC, mixed]}
  \item Holl M., et al., Phys.\ Rev.\ C \textbf{105}, 034301 (2022), DOI: \href{https://doi.org/10.1103/PhysRevC.105.034301}{10.1103/PhysRevC.105.034301}. \texttt{[F13/PDC, implicit]}
  \item Wang H., et al., Phys.\ Lett.\ B \textbf{843}, 138038 (2023), DOI: \href{https://doi.org/10.1016/j.physletb.2023.138038}{10.1016/j.physletb.2023.138038}. \texttt{[F13/PDC, implicit]}
  \item Duer M., et al., Nature \textbf{606}, 678 (2022), DOI: \href{https://doi.org/10.1038/s41586-022-04827-6}{10.1038/s41586-022-04827-6}. \texttt{[F13/PDC, used for $\alpha$ (note exception)]}
  \item Corsi A., et al., Phys.\ Lett.\ B \textbf{797}, 134843 (2019). \texttt{[F13/PDC, implicit]}
  \item Enciu M., et al., Phys.\ Rev.\ Lett.\ \textbf{129}, 262501 (2022), DOI: \href{https://doi.org/10.1103/PhysRevLett.129.262501}{10.1103/PhysRevLett.129.262501}. \texttt{[F13/PDC, implicit]}
  \item Linh B.\ D., et al., Phys.\ Rev.\ C \textbf{109}, 034312 (2024), DOI: \href{https://doi.org/10.1103/PhysRevC.109.034312}{10.1103/PhysRevC.109.034312}. \texttt{[F13/PDC, implicit]}
  \item Pohl T., et al., Phys.\ Rev.\ Lett.\ \textbf{130}, 172501 (2023), DOI: \href{https://doi.org/10.1103/PhysRevLett.130.172501}{10.1103/PhysRevLett.130.172501}. \texttt{[F13/PDC, implicit]}
\end{itemize}

\subsection{Excluded / context-only}
\begin{itemize}
  \item Kubota Y., et al., Phys.\ Rev.\ Lett.\ \textbf{125}, 252501 (2020), DOI: \href{https://doi.org/10.1103/PhysRevLett.125.252501}{10.1103/PhysRevLett.125.252501}. \texttt{[exclude --- uses dedicated RPD not PDC]}
  \item Tanaka J., et al., Science \textbf{371}, 260 (2021), DOI: \href{https://doi.org/10.1126/science.abe4688}{10.1126/science.abe4688}. \texttt{[exclude --- RCNP, not SAMURAI]}
  \item Taniuchi R., et al., Nature \textbf{569}, 53 (2019), DOI: \href{https://doi.org/10.1038/s41586-019-1155-x}{10.1038/s41586-019-1155-x}. \texttt{[F8-ZDS, not PDC]}
  \item Doornenbal P., et al., Phys.\ Rev.\ C \textbf{95}, 041301(R) (2017), DOI: \href{https://doi.org/10.1103/PhysRevC.95.041301}{10.1103/PhysRevC.95.041301}. \texttt{[F8-ZDS]}
  \item Atar L., et al., Phys.\ Rev.\ Lett.\ \textbf{120}, 052501 (2018), DOI: \href{https://doi.org/10.1103/PhysRevLett.120.052501}{10.1103/PhysRevLett.120.052501}. \texttt{[exclude --- R3B/LAND at GSI]}
  \item Panin V., et al., Phys.\ Lett.\ B \textbf{753}, 204 (2016). \texttt{[exclude --- R3B/LAND]}
  \item Sekiguchi K., et al., Phys.\ Rev.\ C \textbf{89}, 064007 (2014), DOI: \href{https://doi.org/10.1103/PhysRevC.89.064007}{10.1103/PhysRevC.89.064007}. \texttt{[exclude --- RIBF dp polarimetry/SMART chamber, not SAMURAI/PDC]}
  \item Sekiguchi K., et al., Phys.\ Rev.\ C \textbf{96}, 064001 (2017), DOI: \href{https://doi.org/10.1103/PhysRevC.96.064001}{10.1103/PhysRevC.96.064001}. \texttt{[exclude --- RIBF dp polarimetry/SMART chamber, not SAMURAI/PDC]}
\end{itemize}

\subsection{Reviews and topical collections}
\begin{itemize}
  \item Aumann T., et al., Prog.\ Part.\ Nucl.\ Phys.\ \textbf{118}, 103847 (2021), DOI: \href{https://doi.org/10.1016/j.ppnp.2021.103847}{10.1016/j.ppnp.2021.103847}.
  \item Panin V., Aumann T., Bertulani C.\ A., Eur.\ Phys.\ J.\ A \textbf{57}, 103 (2021), DOI: \href{https://doi.org/10.1140/epja/s10050-021-00416-9}{10.1140/epja/s10050-021-00416-9}.
  \item Nowacki F., Obertelli A., Poves A., ``The neutron-rich edge of the nuclear landscape: Experiment and theory,'' Prog.\ Part.\ Nucl.\ Phys.\ \textbf{120}, 103866 (2021), DOI: \href{https://doi.org/10.1016/j.ppnp.2021.103866}{10.1016/j.ppnp.2021.103866}.
  \item Aumann T.\ and Bertulani C.\ A., Prog.\ Part.\ Nucl.\ Phys.\ \textbf{112}, 103753 (2020).
  \item PTEP Symposium contributions on direct reactions with hydrogen targets at the RIBF (2024 preprints):
  \begin{itemize}
    \item Yoshida K.\ and Tanaka J., ``Reaction mechanism of quasi-free knockout processes in exotic RI beam era,'' \href{https://arxiv.org/abs/2412.16649}{arXiv:2412.16649} (submitted to PTEP).
    \item Kahlbow J., ``The southern shore of the island of inversion studied via quasi-free scattering,'' \href{https://arxiv.org/abs/2412.16799}{arXiv:2412.16799} (submitted to PTEP).
    \item Taniuchi R., ``Competition of the shell closure and deformations across the doubly magic $^{78}$Ni,'' \href{https://arxiv.org/abs/2412.16972}{arXiv:2412.16972} (submitted to PTEP).
    \item Tanaka J., Cortés M.\ L., Liu H., Taniuchi R., ``Detectors for next-generation quasi-free scattering experiments at the RIBF,'' \href{https://arxiv.org/abs/2412.17887}{arXiv:2412.17887} (submitted to PTEP).
  \end{itemize}
\end{itemize}

\subsection{Construction proposals and internal notes}
\begin{itemize}
  \item RIBF-TAC05 (2005) SAMURAI construction proposal, \url{https://ribf.riken.jp/RIBF-TAC05/10_SAMURAI.pdf}.
  \item 2012 SAMURAI Construction Proposal, \url{https://ribf.riken.jp/SAMURAI/120425_SAMURAIConstProp.pdf}.
  \item RIKEN tech note \texttt{Detector-PDC.pdf}, \url{https://www.nishina.riken.jp/ribf/SAMURAI/image/Detector-PDC.pdf}.
  \item SAMURAI tecinfo page, \url{https://www.nishina.riken.jp/RIBF/SAMURAI/tecinfo.html}.
  \item RIKEN Accelerator Progress Report archive, \url{https://nishina.riken.jp/researcher/APR/index_e.html}.
\end{itemize}

\subsection{Project-internal references}
\begin{itemize}
  \item \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_air\_20260421\_zh.md} --- \texttt{[superseded, stage A]}
  \item \texttt{docs/reports/reconstruction/momentum\_reco/ms\_ablation/ms\_ablation\_mixed\_20260422\_zh.md} --- \texttt{[current, stage A$'$ rev2]}
  \item \texttt{docs/reports/reconstruction/momentum\_reco/rk/rk\_error\_analysis\_deep\_dive\_20260426\_zh.pdf}
  \item \texttt{docs/reports/reconstruction/momentum\_reco/rk/rk\_reconstruction\_status\_20260416\_zh.pdf}
  \item \texttt{docs/reports/reconstruction/track\_reco/pdc/pdc\_reconstruction\_uncertainty\_detailed.pdf}
  \item \texttt{smsimulator5.5/CLAUDE.md} and \texttt{dpol/CLAUDE.md} --- project guides
  \item \texttt{libs/analysis\_pdc\_reco/} --- primary reconstruction framework
\end{itemize}

\end{document}
